UGrade: Autograder for Competitive Programming Using Contestant PC as Worker

### 2019-07-01 src/paper.tex
fix verbs

Currently, most of the online judges use autograder to evaluate contestants' submissions. According to \cite{danutamalms}, autograder is a system that compiles, executes and evaluate source code. Evaluates source code manually takes three minutes while using autograder only need ten seconds. By using autograder, contestants can receive grading feedback faster and reduce the work that needs to be done by juries. Basically, the autograder evaluate the source code by compiles the source code and executes the compiled program using predefined test-cases. The output of contestant's solution program compared to the predefined test-case and then graded. This evaluation method is called black-box grading \cite{jordanioi}.

>>>>

Currently, most of the online judges use autograder to evaluate contestants' submissions. According to \cite{danutamalms}, autograder is a system that compiles, executes and evaluates source code. Evaluating source code manually takes three minutes while using autograder only need ten seconds. By using autograder, contestants can receive grading feedback faster and reduce the work that needs to be done by juries. Basically, the autograder evaluates the source code by compiling the source code and executing the compiled program using predefined test-cases. The output of contestant's solution program is compared to the predefined test-case and then graded. This evaluation method is called black-box grading \cite{jordanioi}.
